---
title: "Short-Time-AOI-Based-Scanpath-Aggregation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Short-Time-AOI-Based-Scanpath-Aggregation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


A group of scanpaths are aggregated through a representative scanpath. The representative scanpath
is formed by linking the short time AOIs as shown follows:

```{r, out.width = "500px"}
filepath = system.file('stimulus/shorttimeAOI3D2D.png', package = "scanpathAggr")
knitr::include_graphics(filepath)
```


Load the package after install
```{r}
library(scanpathAggr)
```



Find a reprensentative scanpath, the scanpaths should be a data.frame containing the following 4 or 6 column, including 

(1) Participant, which is the name or id for the participants 
(2) Fixation_Position_X_px 
(3) Fixation_Position_Y_px 
(4) Event_Start_Trial_Time_ms, start time of fixation in seconds
(5) Event_Ende_Trial_Time_ms, end time of the fixation in seconds
(6) Duration, duration of the fixation in seconds 

Each row represents a fixation, and fixations are in temporal order. If there are no Event_Start_Trial_Time_ms and Event_Ende_Trial_Time_ms, this function will create fake start and end time for the fixations.

## Data containing 6 columns:
```{r}
data(scanpath_MIT1003_i1182314083)
reprensentScanpath = scanpathAggr(scanpath_MIT1003_i1182314083, 3, theta = 0.2)
```


## Data containing 4 columns (without start and end time of the fixations):
```{r}
data(scanpath_OSIE_1001)
reprensentScanpath = scanpathAggr(scanpath_MIT1003_i1182314083, 3, theta = 0.2)
```






Show the reprensentative scanpath 
```{r, out.width = "700px", , out.height="400px"}
reprensentScanpath = scanpathAggr(scanpath_MIT1003_i1182314083, 3, theta = 0.2)
stimuluspath = system.file('stimulus/i1182314083.jpeg', package = "scanpathAggr")
scanpathVisualisation(scanpath_MIT1003_i1182314083, reprensentScanpath, stimuluspath)
```



Increase $\theta$ to simplify the reprensentative scanpath
```{r, out.width = "700px", , out.height="400px"}
data(scanpath_MIT1003_i1182314083)
reprensentScanpath = scanpathAggr(scanpath_MIT1003_i1182314083, 3, theta = 0.6)
scanpathVisualisation(scanpath_MIT1003_i1182314083, reprensentScanpath, stimuluspath)
```


Simplify the reprensentative scanpath post hoc 
```{r, out.width = "700px", , out.height="400px"}
data(scanpath_MIT1003_i1182314083)
reprensentScanpath = scanpathAggr(scanpath_MIT1003_i1182314083, 3, theta = 0.2, simplify = TRUE)
scanpathVisualisation(scanpath_MIT1003_i1182314083, reprensentScanpath, stimuluspath)
```








